---
title: "04: Indexing"
author: "Charlie Lindgren"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Indexing

In R, you can select elements from a vector, list, or data frame using indexing.

### Vector Indexing

```{r}
# A numeric vector
numeric_vector <- c(10, 20, 30, 40, 50)

# Select the third element
numeric_vector[3]

# Select the first and third elements
numeric_vector[c(1, 3)]
```

### List Indexing

```{r}
# A list
my_list <- list(
  name = "Charlie",
  age = 30,
  is_student = FALSE
)

# Select the 'age' element
my_list$age
my_list[["age"]]
```

## Exercises

1. Create a numeric vector named `my_vector` with the numbers 1 to 10.

```{r}
# Your code here
```

2. Select the 5th element of `my_vector`.

```{r}
# Your code here
```

3. Select the 2nd, 4th, and 6th elements of `my_vector`.

```{r}
# Your code here
```

4. Create a list named `my_list` with the same elements as in the example. Select the `name` element.

```{r}
# Your code here
```

5. Create a 3x3 matrix named `my_matrix` with numbers from 1 to 9.

```{r}
# Your code here
```

6. Extract the first row of `my_matrix`.

```{r}
# Your code here
```

7. Extract the last column of `my_matrix`.

```{r}
# Your code here
```

8. Extract the diagonal elements of `my_matrix`.

```{r}
# Your code here
```

9. Extract the element in the second row and third column of `my_matrix`.

```{r}
# Your code here
```

10. Extract the elements in the first and third rows and the second and third columns of `my_matrix`.

```{r}
# Your code here
```

11. Extract the elements from `my_matrix` that are greater than 5.

```{r}
# Your code here
```

## Solutions

[Click here for the solutions](indexing_answers.Rmd)