---
title: "05: Functions"
author: "Charlie Lindgren"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Functions

In R, a function is a block of code that performs a specific task. You can define your own functions in R.

```{r}
# A simple function to add two numbers
add_numbers <- function(x, y) {
  return(x + y)
}

# Call the function
add_numbers(5, 10)
```

## Exercises

1. Write a function named `square_number` that takes a number as input and returns its square.

```{r}
# Your code here
```

2. Write a function named `get_greeting` that takes a name as input and returns a greeting message (e.g., "Hello, Charlie!").

```{r}
# Your code here
```

3. Write a function named `calculate_mean` that takes a numeric vector as input and returns its mean.

```{r}
# Your code here
```

4. Write a function that will return the sum of 2 integers.

```{r}
# Your code here
```

5. Write a function that will return `TRUE` if a given integer is inside a vector.

```{r}
# Your code here
```

6. Write a function that, given a data frame, will print the name of each column and the class of data it contains (e.g., "Variable1 is Numeric").

```{r}
# Your code here
```

7. Create a function that, given a vector and an integer, will return how many times the integer appears inside the vector.

```{r}
# Your code here
```

8. Create a function that, given a numeric vector, will print the mean and the standard deviation. It will optionally also print the median if the vector has an odd number of elements.

```{r}
# Your code here
```

9. Create a function that, given an integer, will calculate how many divisors it has (other than 1 and itself) and print the divisors.

```{r}
# Your code here
```

10. Create a function that, given a data frame and a value (number or character), will return the data frame with all occurrences of that value changed to `NA`.

```{r}
# Your code here
```

## Solutions

[Click here for the solutions](functions_answers.Rmd)