---
title: "08: Loops"
author: "Charlie Lindgren"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Loops

In R, loops are used to repeat a block of code multiple times. The most common type of loop is the `for` loop.

```{r}
# A for loop that prints the numbers 1 to 5
for (i in 1:5) {
  print(i)
}
```

## Exercises

1. Write a `for` loop that prints the first 5 even numbers.

```{r}
# Your code here
```

2. Create a numeric vector named `my_vector` with the numbers 1 to 10. Write a `for` loop that iterates over `my_vector` and prints the square of each number.

```{r}
# Your code here
```

3. Create a character vector named `my_colors` with your three favorite colors. Write a `for` loop that iterates over `my_colors` and prints each color.

```{r}
# Your code here
```

4. Write a `for` loop that prints the numbers from 1 to 10.

```{r}
# Your code here
```

5. Write a `for` loop that prints the even numbers from 1 to 10.

```{r}
# Your code here
```

6. Write a program that calculates the factorial of a given number (e.g., 5!) using a `for` loop.

```{r}
# Your code here
```

7. Write a program that prints the Fibonacci sequence up to a given number of terms (e.g., 10 terms) using a `for` loop.

```{r}
# Your code here
```

8. Write a program that prints the multiplication table of a given number (e.g., 7) using a `for` loop. The output should be in a human-readable format (e.g., "7 x 1 = 7").

```{r}
# Your code here
```

9. Write a program that prints the prime numbers up to a given number (e.g., 20) using a `for` loop and conditional statements.

```{r}
# Your code here
```

10. Write a program that prints the sum of the digits of a given number (e.g., 123) using a `for` loop.

```{r}
# Your code here
```

## Solutions

[Click here for the solutions](loops_answers.Rmd)