---
title: "07: Conditionals"
author: "Charlie Lindgren"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Conditionals

In R, conditionals are used to control the flow of execution based on certain conditions. The most common conditional statement is the `if-else` statement.

```{r}
# An if-else statement
x <- 10
if (x > 5) {
  print("x is greater than 5")
} else {
  print("x is not greater than 5")
}
```

## Exercises

1. Write an `if-else` statement that checks if a number is positive or negative.

```{r}
# Your code here
```

2. Write an `if-else` statement that checks if a person is eligible to vote (age >= 18).

```{r}
# Your code here
```

3. Write a function named `check_grade` that takes a numeric grade as input and returns "Pass" if the grade is 50 or above, and "Fail" otherwise.

```{r}
# Your code here
```

4. Write a program that checks if a given number is even or odd.

```{r}
# Your code here
```

5. Write a program that checks if a given number is positive, negative, or zero.

```{r}
# Your code here
```

6. Write a program that checks if a given string is empty or not.

```{r}
# Your code here
```

7. Write a program that checks if a given vector contains a specified element.

```{r}
# Your code here
```

8. Write a program that checks if a given number is between two other numbers.

```{r}
# Your code here
```

9. Write a program that checks if a given year is a leap year.

```{r}
# Your code here
```

10. Write a program that checks if a given number is a prime number.

```{r}
# Your code here
```

11. Write a program that assigns grades (A, B, C, D, F) based on a given score (0-100).

```{r}
# Your code here
```

12. Write a program that checks if a given number is a perfect square.

```{r}
# Your code here
```

13. Write a program that checks if a given number is a palindrome.

```{r}
# Your code here
```

## Solutions

[Click here for the solutions](conditionals_answers.Rmd)