---
title: "02: Lists"
author: "Charlie Lindgren"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Lists

In R, a list is a generic vector containing other objects. For example, a list can contain a numeric vector, a character vector, and a logical vector. The `list()` function is used to create a list.

```{r}
# A list containing a numeric vector, a character vector, and a logical vector
my_list <- list(
  numbers = c(1, 2, 3),
  characters = c("a", "b", "c"),
  logicals = c(TRUE, FALSE, TRUE)
)
print(my_list)
```

## Exercises

1. Create a list named `my_info` that contains your name, your age, and whether you are a student or not.

```{r}
# Your code here
```

2. Access the `age` element from the `my_info` list.

```{r}
# Your code here
```

3. Add a new element to the `my_info` list called `hobbies` that contains a vector of your hobbies.

```{r}
# Your code here
```

4. Create an empty list named `my_empty_list`.

```{r}
# Your code here
```

5. Get the length of the `my_info` list.

```{r}
# Your code here
```

6. Get the first element of the `my_info` list.

```{r}
# Your code here
```

7. Get the last element of the `my_info` list.

```{r}
# Your code here
```

8. Get the elements from the second to the third position in the `my_info` list.

```{r}
# Your code here
```

9. Remove the `is_student` element from the `my_info` list.

```{r}
# Your code here
```

## Solutions

[Click here for the solutions](lists_answers.Rmd)