---
title: "06: Logical Operators"
author: "Charlie Lindgren"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Logical Operators

In R, logical operators are used to perform logical operations. The most common logical operators are `&` (AND), `|` (OR), and `!` (NOT).

```{r}
# Logical AND
TRUE & TRUE
TRUE & FALSE

# Logical OR
TRUE | FALSE
FALSE | FALSE

# Logical NOT
!TRUE
!FALSE
```

## Exercises

1. Create a numeric vector named `my_vector` with the numbers 1 to 10.

```{r}
# Your code here
```

2. Use a logical operator to select the numbers in `my_vector` that are greater than 5.

```{r}
# Your code here
```

3. Use a logical operator to select the numbers in `my_vector` that are less than or equal to 3.

```{r}
# Your code here
```

4. Use logical operators to select the numbers in `my_vector` that are greater than 3 AND less than 7.

```{r}
# Your code here
```

5. Create a character vector named `my_fruits` with "apple", "banana", "orange", "apple", "grape". Extract the elements that are equal to "apple".

```{r}
# Your code here
```

6. Create a data frame with `name` and `age` columns. Extract the rows where `age` is greater than 25.

```{r}
# Your code here
```

7. Using the same data frame, extract only the `name` column for rows where `age` is greater than 25.

```{r}
# Your code here
```

## Solutions

[Click here for the solutions](logical_operators_answers.Rmd)