---
title: "03: Factors"
author: "Charlie Lindgren"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction to Factors

In R, a factor is a vector that can take on only a limited number of different values. Such a vector is often referred to as a categorical variable. The `factor()` function is used to create a factor.

```{r}
# A factor of eye colors
eye_colors <- factor(c("brown", "blue", "green", "blue", "brown", "brown"))
print(eye_colors)
```

## Exercises

1. Create a factor named `education_levels` with the following education levels: "High School", "Bachelor's", "Master's", "PhD", "Bachelor's".

```{r}
# Your code here
```

2. Display the levels of the `education_levels` factor.

```{r}
# Your code here
```

3. Create an ordered factor for `education_levels`.

```{r}
# Your code here
```

4. Create a factor of movie ratings with the following ratings: "Good", "Great", "Good", "Excellent", "Good", "Bad". The levels should be "Bad", "Good", "Great", "Excellent".

```{r}
# Your code here
```

5. Create a data frame with two columns: `student` (a character vector of student names) and `grade` (a factor with levels "A", "B", "C", "D", "F").

```{r}
# Your code here
```

6. Subset the data frame to only include students with a grade of "A" or "B".

```{r}
# Your code here
```

## Solutions

[Click here for the solutions](factors_answers.Rmd)