---
title: "Analyzing Cosmetics Data (RDS)"
author: "Charlie Lindgren"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(ggplot2)
library(readr)
```

## Introduction

This document demonstrates how to load, explore, transform data from a CSV file, and then save and load it as an RDS file in R, with a focus on `dplyr` for modern data analysis workflows.

## Exercises

### Exercise 1: Load the Data

Load the `most_used_beauty_cosmetics_products_extended.csv` dataset into an R data frame. Use `read_csv()` from the `readr` package for this.

```{r}
# Your code here
```

### Exercise 2: Explore the Data

Display the structure of the `cosmetics` data frame, get a statistical summary, and check the unique values of the `Product_Size` column.

```{r}
# Your code here
```

### Exercise 3: Data Transformation - Product Size

Transform the `Product_Size` column into an ordered factor with appropriate levels.

```{r}
# Your code here
```

### Exercise 4: Save Data to RDS

Save the transformed `cosmetics` data frame to an RDS file named `cosmetics.rds` in the `_rds` directory.

```{r}
# Your code here
```

### Exercise 5: Load Data from RDS

Load the `cosmetics.rds` file back into R, but name the new object `cosmetics_from_rds`.

```{r}
# Your code here
```

### Exercise 6: Compare Data Frames

Use the `identical()` function to compare the original `cosmetics` data frame with `cosmetics_from_rds` to ensure no data loss or alteration.

```{r}
# Your code here
```

### Exercise 7: Data Visualization - Price Distribution

Create a histogram of the `Price_USD` column from `cosmetics_from_rds` to visualize its distribution.

```{r}
# Your code here
```

## Solutions

[Click here for the solutions](analyze_cosmetics_rds_answers.Rmd)
